---
title: "hw01-Tianran-Li"
author: "Grace Li (Tianran)"
date: "February 20, 2018"
output: github_document
---

```{r}
read.csv('imports-85.data')
```


```{r}
column_names <- c('symboling', 'normalized_losses', 'make', 'fuel_type', 'aspiration', 'num_of_doors', 'body_style','drive_wheels', 'engine_location', 'wheel_base', 'length', 'width', 'height', 'curb_weight', 'engine_type', 'num_of_cylinders', 'engine_size', 'fuel_system', 'bore', 'stroke', 'compression_ratio', 'horsepower', 'peak_rpm', 'city_mpg', 'highway_mpg', 'price' )
column_names
column_types <- c('double', 'double', 'character', 'character', 'character', 'character', 'character', 'character', 'character', 'double', 'double', 'double', 'double', 'integer', 'character', 'character', 'integer', 'character', 'double', 'double', 'double','integer','integer','integer','integer','integer' )
```


```{r}
normal_read <- read.csv(
    'imports-85.data',
    col.names = column_names,
    colClasses = column_types,
    sep = ",",
    na.strings = '?'
)

str(normal_read)
normal_read
```

```{r}
library('readr')
readr_read <- read_csv('imports-85.data' , col_names = column_names, col_types = cols('d', 'd', 'c', 'c', 'c', 'c', 'c', 'c', 'c', 'd', 'd', 'd', 'd', 'i', 'c', 'c', 'i', 'c', 'd', 'd', 'd', 'i', 'i', 'i', 'i', 'i'))
str(readr_read)
readr_read
```



##Technical Questions

a. The first row of the data file becomes the column names if you don't provide a vector of column names.
b. The function puts V1- V26 as the column names.
c. The data type of those columns that contain '?' gets converted to factors if you don't specify how missing values are codified. 
d. The data frame imported in the second option is bigger since each column's data type is specified, so the converted types will occupy more space than the default data type.
e. The data type of every entry in dat will be converted to charactor. The matrix will consist of 26 charactor vectors, with 205 entries each, but the matrix will only show the first 38 entries (or to its max).


##Practice base plotting

```{r}
library(plyr)
hist(normal_read[ ,'price'], col = 'purple')
boxplot(normal_read[ ,'horsepower'], horizontal =  TRUE)
counted_table = count(normal_read, 'body_style')
sorted_table = counted_table[order(counted_table$freq, decreasing = TRUE), ]
barplot(sorted_table$freq, names.arg = sorted_table$body_style)
stars(normal_read[normal_read$aspiration == 'turbo' , c("wheel_base", "length", "width", "height", "price")])
```

##Summaries

```{r}
gas_cars <- normal_read[normal_read$fuel_type == 'gas', ]
mean(gas_cars$price, na.rm = TRUE)
```

```{r}
diesel_cars <- normal_read[normal_read$fuel_type == 'diesel', ]
mean(diesel_cars$price, na.rm = TRUE)
```

```{r}
normal_read[normal_read$num_of_cylinders == 'twelve', 'make']
```

```{r}
counted_diesel = count(diesel_cars, 'make')
counted_diesel[which.max(counted_diesel$freq), "make"]
```

```{r}
normal_read[which.max(normal_read$horsepower), "price"]
```

```{r}
city_bottom_ten = tail((normal_read[order(normal_read$city_mpg, decreasing = TRUE), ]), n = nrow(normal_read)/10 )
city_bottom_ten[ ,'city_mpg']
highway_top_ten =  head((normal_read[order(normal_read$highway_mpg, decreasing = TRUE), ]), n = nrow(normal_read)/10 )
highway_top_ten[ ,'highway_mpg' ]
```

```{r}
median(city_bottom_ten$price, na.rm = TRUE)
```


##Technical Questions about data frames

a. attempting to use the name of a column that does not exist will return a NULL
b. mtcars[ ,mpg] fails to return the vector mpg
c. The command fails because there is no object named mpg in environment. mpg is the name of the column on the data frame, but mpg is not assigned to any particular object.
d. YES, you can include an R list as a 'column' of a data frame. A data frame is a list, it can contain other lists.
e. The command returns the list of vectors that make up the data frame. 
f. data.frame can be used to conver abc into a data frame.



##Correlations

```{r}
read = na.omit(normal_read)

quantitative = Filter(is.numeric, read)
qdat = quantitative[ ,3:ncol(quantitative)]
correlation_matrix = cor(qdat)
library(corrplot)
corrplot(correlation_matrix, method = 'circle')
corrplot(correlation_matrix, method = 'ellipse')
```
The strongest positive correlation is between an object and itself. 
The strongest negative correlatio is between city_mpg or highway_mpg and horsepower.
In some combinations, the correlation between the two vectors is close to zero.



Principal Component Analysis

8.1) 
```{r}
Qdat_PCA = prcomp(qdat, scale = TRUE)
names(Qdat_PCA)
eigenvalues = Qdat_PCA$sdev^2
percentages = eigenvalues*100/sum(eigenvalues)
cum_percentages = cumsum(percentages)
data.frame(eigenvalues, percentages, cum_percentages)
```

About 79.60% of variation is "captured" by the first three components.

8.2)

```{r}
df_PCA = data.frame(Qdat_PCA$x)
plot(df_PCA$PC1, df_PCA$PC2, type = 'p')
plot(Qdat_PCA, type = 'l')
```

```{r}
Print_PCA = princomp(qdat, cor = TRUE)
Loadingdf = data.frame(unclass(Print_PCA$loadings))
plot(Loadingdf$Comp.1, Loadingdf$Comp.2, type = 'p')
plot(Print_PCA, type = 'l')
```
For both prcomp and princomp, the first loading has the most variance, and can represent more of the data than any other object in loading.
For Princomp, the loadings are perpendicular to each other.

